Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-04-06 Report/time_correlated.tex
adhi

Fig. \subref*{fig-review} plots the average of the total number of backlogged packets left out in the system after each transmission instant, \textit{i.e}, \me{\mathbf{\mathrm{E}}_i \, [ \Sigma_k \left [ Q_k(i) - t_k(i) \right ]^+ ]}. Unlike the \ac{Q-WSRM} scheme, the average backlogged packets of the \me{\ell_2} \ac{JSFRA} scheme is comparable to the \ac{Q-WSRME} approach for all average arrival rates due to the explicit rate constraints \eqref{eqn-3.1.4}. However, when \me{A_k \geq 7} bits in Fig. \subref*{fig-review}, both \ac{Q-WSRM} and \ac{Q-WSRME} schemes perform the same since the problem of over-allocation is negligible. The performance of the \me{\ell_1} \ac{JSFRA} scheme outperforms all other schemes in terms of the average number of residual packets due to the greedy allocation at each instant.

>>>>

Fig. \subref*{fig-review} plots the average of the total number of backlogged packets left out in the system after each transmission instant, \textit{i.e}, \me{\mathbf{\mathrm{E}}_i \, [ \sum_k \left [ Q_k(i) - t_k(i) \right ]^+ ]}. Unlike the \ac{Q-WSRM} scheme, the average backlogged packets of the \me{\ell_2} \ac{JSFRA} scheme is comparable to the \ac{Q-WSRME} approach for all average arrival rates due to the explicit rate constraints \eqref{eqn-3.1.4}. However, when \me{A_k \geq 7} bits in Fig. \subref*{fig-review}, both \ac{Q-WSRM} and \ac{Q-WSRME} schemes perform the same since the problem of over-allocation is negligible. The performance of the \me{\ell_1} \ac{JSFRA} scheme outperforms all other schemes in terms of the average number of residual packets due to the greedy allocation at each instant.
